Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-03-15 paperDistance/paper.tex
adjust outline

% # To-do list
% - We need a standard name for the \tgas--\tmass--\PanSTARRS\ Intersection.
% - zeroth draft the introduction
% - zeroth draft the method section
% - zeroth draft the assumptions list
% - reformat single-column

\documentclass[modern]{aastex61}
\usepackage{amsmath}
\setlength{\parindent}{\baselineskip}

@@

\title{Improving \textsl{Gaia} parallaxes
       with a data-driven model of the color--magnitude diagram}

@@

Talk about structures in CMD; red bump - acknowledge Ana ! s
What's That Feature ?!!

Fraction of stars in various parts of the diagram?

@@

\bibliography{lmanders}
%\begin{thebibliography}{}
%\end{thebibliography}

>>>>

% # To-do list
% - We need a standard name for the \tgas--\tmass--\PanSTARRS\ Intersection.
% - zeroth draft / re-write the method section
% - make a ``why does this work'' section

\documentclass[modern]{aastex61}
\usepackage{amsmath}
\setlength{\parindent}{\baselineskip} % trust me!
\renewcommand{\twocolumngrid}{} % trust me!

@@

\title{Improving \textsl{Gaia} parallaxes
       with a data-driven model \\
       of the color--magnitude diagram}

@@

Talk about structures in CMD; red bump - acknowledge Ana ! s
What's That Feature? Similarly; Fraction of stars in various parts of the diagram?

@@

\bibliography{lmanders}
